---
title: "cousework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
getwd()

```
```{r}
install.packages("maptools")
install.packages("RColorBrewer")
install.packages("classInt")
install.packages("OpenStreetMap")
install.packages("sp")
install.packages("rgeos")
install.packages("tmap")
install.packages("tmaptools")
install.packages("sf")
install.packages("rgdal")
install.packages("geojsonio")
install.packages("png")
library(knitr)
library(png)
library(maptools)
library(RColorBrewer)
library(classInt)
library(OpenStreetMap)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
hertfordshire_path <- "D:\\UCL TERM 1\\GIS/cousework1\\cousework gis arcgis.png"
hertfordshire <- readPNG(hertfordshire_path, native = TRUE, info = TRUE)
include_graphics(hertfordshire_path)
EW <- geojson_read("http://geoportal.statistics.gov.uk/datasets/8edafbe3276d4b56aec60991cbddda50_2.geojson", what = "sp")
qtm(london_osm) + 
  tm_shape(BoroughDataMap) + 
  tm_polygons("Rate.of.JobSeekers.Allowance..JSA..Claimants...2015", 
              style="jenks",
              palette="YlOrBr",
              midpoint=NA,
              title="Rate per 1,000 people",
              alpha = 0.5) + 
  tm_compass(position = c("left", "bottom"),type = "arrow") + 
  tm_scale_bar(position = c("left", "bottom")) +
  tm_layout(title = "Job seekers' Allowance Claimants", legend.position = c("right", "bottom"))
```

When comparing the spatial data visualization production process through RStudio and ArcGIS, some strengths and weakness of these two softwares could to critical review. The strengths and weakness of RStudio and ArcGIS will be separated to discussion.

The RStudio is a statistical computing professional software, the ArcGIS is a professional integrated geographic information management system. Therefore, the RStudio has more statistics processing function in other computing fields than ArcGIS. 

The RStudio provides open source and open packages to public. As a computing software, it could use C++ language to processing several kinds of data. The advantages of RStudio are focus on statistics management and processing. The first one is that it could import web page data directly. It is extremely useful for users, because this function greatly facilitates the extraction of data for users. The second one is that it could use open packages with different functions to manage statistics, it is more professional, easier and convenient than ArcGIS. The Third one is that its data processing capabilities are more direct and effective, only need fixed programming principles and packages. The fourth one is that it is simpler to do interactive maps, and it could be plotted maps on a large number of scales, or to arrange the number of plots map as needed. The fifth one is that the code of plotting map has a fixed format, if you could like to create a similar visual map, the users could copy a similar code. However, the weakness of RStudio is clear. Due to the RStudio is a extremely professional data processing software, it is difficult to study for the first users when they taught it initially. The C++ code is concrete and complex, it is requires some logic to create the code work correctly. It required that the users has a little logic basis. The second weakness is that its steps and processes are cumbersome when importing statistics and install the packages which you needed. You need install the different packages separated then “library” them. The third weakness is that the RStudio does not suitable for modifying data at any time especially when the users already visualized the spatial data. When users could like to ,modify the current data and re-visualize the data, users needs to write code to modify the statistics first, then to write code to re-visualize the data again.

For the ArcGIS, it is a professional geographic information management software, therefore it has more strengths than RStudio on visualizing spatial data. During the process of plotting map, it is simpler, easier and easier to understand for beginners to master. The geographic statistics is more easier to management, it has a complete data processing system, including basic data processing, data format transfer, data analysis and data output. In addition, due to its attributes, the data in ArcGIS is more suitable for modification and management at any time, and it does not need to modify the spatial map that has been visualized as well. The visual spatial map and data changes are automatically consistent. However, the disadvantages of ArcGIS is that it is not suitable for a large number of plotting, it cannot create two or more map in one plot like RStudio.

To conclude, the RStudio and ArcGIS has their own advantages and weakness on different fields. For the data management, the RStudio has more benefits, the ArcGIS has more benefits for professional geographic visualizing spatial data map.
